THESIS PROJECT PROPOSAL

### 2019-11-10 project_ashish/paper1.tex
Add files via upload
Update paper1.tex

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{./tq.png}
	\caption{Higgs production using the top quark (left) and W boson (right).}
	\label{figure 4}
\end{figure}

@@

 \begin{figure}[H]
  \centering
   \includegraphics[width=\columnwidth]{./cms13.png}
  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines)..}
   \label{figure 9}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{./tq.png}
	\caption{Higgs boson production using the top quark (left) and W boson (right).}
	\label{figure 4}
\end{figure}

@@

 \begin{figure}[H]
  \centering
   \includegraphics[width=\columnwidth]{./cms13.png}
  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
   \label{figure 9}
\end{figure}
